---
title: "Wave 1 Victoria Linkage"
author: "Daniel Fuller"
output:
  github_document:
    keep_html: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(kableExtra)
library(lubridate)
```

# Victoria Wave 1 Linkage Files

### Read in Data

Reading in the data. Here we are reading in two files

- `linkage_for_ingest_vic_w1.csv` which is our main file
- `lut_vic.csv` which is a look up table for looking up previous versions of the health and VERITAS ID variables. These will not be used after Wave 1. 

```{r}
setwd("/Users/dlf545/Documents/ForDan_Linkages_072023")
vic_w1 <- read_delim("linkage_for_ingest_vic_w1.csv", delim = ";")
lut_vic <- read_delim("lut_vic.csv", delim = ",")
```

### Fix dates

Linkage file used by Jeff is very messy. First step is to standardize dates

```{r}
vic_w1 <- separate(vic_w1, col = dates, into = c("sd_start_1_messy", "sd_end_1_messy"), sep = "-")
```

Fixing the start dates for SenseDoc

```{r}
vic_w1$sd_start_1 <- parse_date_time(vic_w1$sd_start_1_messy, orders = c("md", "dm"))
year(vic_w1$sd_start_1) <- 2017
```

Fixing the end dates for SenseDoc

```{r}
vic_w1$sd_end_1 <- parse_date_time(vic_w1$sd_end_1_messy, orders = c("mdy", "dmy", "md", "dm"))
```

Spot checked text dates with parsed dates 

```{r}
date_review <- select(vic_w1, sd_start_1_messy, sd_end_1_messy, sd_start_1, sd_end_1)
```

Looks good. 

## Join LUT with vix_w1 

Join Benoit's LUT and check if IDs match #309 records 

```{r}
vic_w1 <- full_join(vic_w1, lut_vic, by="interact_id")
vic_w1$match <- ifelse(vic_w1$treksoft_pid == vic_w1$treksoft_id, "yes", "no")
table(vic_w1$match)
```

Complete match on PID confirmed

### Harmonize Columns

```{r}
vic_w1 <- rename(vic_w1, ethica_id = ethica_id.x)
```

Remove text notes in Ethica id and Sensedoc ID field 

```{r}
non_numeric <- grepl("[^0-9]", vic_w1$ethica_id)
vic_w1$ethica_id[non_numeric] <- NA
```

### Flag test accounts

```{r}
ethica_tests <- c("1451", "2036", 
                  "5256", "1454", 
                  "8911", "1469",
                  "1462", "9321", 
                  "12641", "12638", 
                  "12617", "1470",
                  "4579", "5367",
                  "5399","3962")
```

```{r}
vic_w1 <- vic_w1 %>%
  mutate(test = ifelse(ethica_id %in% ethica_tests, 1, 0)) 
```

### Adding columns

```{r}
vic_w1$plg_id <- NA
vic_w1$dropout <- NA
vic_w1$spam_participant <- NA
vic_w1$wave <- 1
```

### Selecting variables

```{r}
vic_w1 <- select(vic_w1, interact_id, treksoft_pid, treksoft_uid, ethica_id, sd_id_1, sd_firmware_1, sd_start_1, sd_end_1, sd_id_2, sd_firmware_2, sd_start_2, sd_end_2, data_disposition, plg_id, dropout, wave, test, spam_participant)
```

### Write clean file

```{r}
write.csv(vic_w1, file= "linkage_vic_w1.csv")
```