---
title: "Wave 2 Victoria Linkage"
author: "Daniel Fuller"
output:
  github_document:
    keep_html: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(kableExtra)
```

# Victoria Wave 2 Linkage Files

### Read in Data

Reading in the data. Here we are reading in two files

- `linkage_for_ingest_vic_w2.csv` which is our main file
- `lut_vic2.csv` which is a look up table for looking up previous versions of the health and VERITAS ID variables. These will not be used after Wave 1. 

```{r}
setwd("/Users/dlf545/Documents/ForDan_Linkages_072023")
vic <- read_delim("linkage_for_ingest_vic_w2.csv", delim = ";", name_repair = "universal")
lut_vic <- read_delim("lut_vic2.csv", delim = ",", name_repair = "universal")
```

```{r}
vic_w2 <- full_join(vic, lut_vic, by = "interact_id")
colnames(vic_w2)
```

### Rename variables

```{r}
vic_w2 <- rename(vic_w2, 
                 sd_id_1 = sensedoc_serial,
                 ethica_id = Ethica.ID,
                 sd_start_1 = start_date,
                 sd_end_1 = end_date,
                 sd_firmware_1 = sensedoc_revno)
```

### Flag test accounts

```{r}
ethica_tests <- c("1451", "2036", 
                  "5256", "1454", 
                  "8911", "1469",
                  "1462", "9321", 
                  "12641", "12638", 
                  "12617", "1470",
                  "4579", "5367",
                  "5399","3962")
```

```{r}
vic_w2 <- vic_w2 %>%
  mutate(test = ifelse(ethica_id %in% ethica_tests, 1, 0)) 
```

### Adding columns

```{r}
vic_w2$dropout <- NA
vic_w2$plg_id <- NA
vic_w2$spam_participant <- NA
vic_w2$wave <- 2
```

### Selecting variables

```{r}
vic_w2 <- select(vic_w2, interact_id, treksoft_pid, treksoft_uid, ethica_id, sd_id_1, sd_firmware_1, sd_start_1, sd_end_1, sd_id_2, sd_firmware_2, sd_start_2, sd_end_2, data_disposition, plg_id, dropout, wave, test, spam_participant)
```

### Write clean file

```{r}
write.csv(vic_w2, file= "linkage_vic_w2.csv")
```


