---
title: "Wave 1 Vancouver Linkage"
author: "Daniel Fuller"
output:
  github_document:
    keep_html: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(kableExtra)
```

# Vancouver Wave 1 Linkage Files

### Read in Data

Reading in the data. Here we are reading in two files

- `linkage_for_ingest_van_w1.csv` which is our main file
- `lut_van.csv` which is a look up table for looking up previous versions of the health and VERITAS ID variables. These will not be used after Wave 1. 

```{r}
setwd("/Users/dlf545/Documents/ForDan_Linkages_072023")
van <- read_delim("linkage_for_ingest_van_w1.csv", delim = ";")
lut_van <- read_delim("lut_van.csv", delim = ",")
```

### Compare IDs between tables

```{r}
van_w1 <- full_join(van, lut_van, by="interact_id")
van_w1$eth_check <- ifelse(van_w1$ethica_id.x == van_w1$ethica_id.y, "yes", "no")
table(van_w1$eth_check)
```

4 ethica IDs not in BT's table but present in mine. Keep longer list of mine.

### Keeping variables

```{r}
van_w1 <- rename(van_w1, 
                 ethica_id = ethica_id.x)
```

### Flag test accounts

```{r}
ethica_tests <- c("1451", "2036", 
                  "5256", "1454", 
                  "8911", "1469",
                  "1462", "9321", 
                  "12641", "12638", 
                  "12617", "1470",
                  "4579", "5367",
                  "5399","3962")
```

```{r}
van_w1 <- van_w1 %>%
  mutate(test = ifelse(ethica_id %in% ethica_tests, 1, 0)) 
```

### Adding columns

```{r}
van_w1$plg_id <- NA
van_w1$spam_participant <- NA
van_w1$wave <- 1

van_w1$treksoft_pid <- as.numeric(van_w1$treksoft_pid)
van_w1$treksoft_uid <- as.numeric(van_w1$treksoft_uid)
```

### Selecting variables

```{r}
van_w1 <- select(van_w1, interact_id, treksoft_pid, treksoft_uid, ethica_id, sd_id_1, sd_firmware_1, sd_start_1, sd_end_1, sd_id_2, sd_firmware_2, sd_start_2, sd_end_2, data_disposition, plg_id, dropout, wave, test, spam_participant)
```


### Write clean file

```{r}
write.csv(van_w1, file= "linkage_van_w1.csv")
```