---
title: "INTERACT | SenseDoc Quality checks"
author: "B. Thierry, Spherelab"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_print: paged
    code_folding: hide
    self_contained: no
    keep_md: true
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
    df_print: kable
---

```{r setup, include=FALSE}
library(tidyverse)
library(DBI)
library(sf)
library(ggmap)
library(cowplot)
library(units)
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 10)
knitr::opts_chunk$set(fig.height = 8)

# Define connection to Cedar DB || Requires a live SSH tunnel
con <- dbConnect(RPostgres::Postgres(), user="btcrchum", port=5433, dbname = "interact_db")

#dbExecute(con, 'SET client_min_messages TO WARNING') # Suppress all notices displayed while computing raster stats
knitr::opts_chunk$set(connection = "con")

```

# QA objectives

Create summary statistics (see `QA` subfolder):

+ date ranges
+ number of days of data per participant
+ min, max, SD distributions
+ GPS locations
+ [Sept. 2025] Step statistics

# Data coverage

## Get data from database

```{sql, output.var="top_1s_agg", cache=TRUE}
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'mtl' city_id, 1 wave_id
		,ts.*, tm.wearing
	FROM top_sd.top_1sec_mtl ts,
		top_sd.top_1min_mtl tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get Mtl / w2
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'mtl' city_id, 2 wave_id
		,ts.*, tm.wearing
	FROM top_sd2.top_1sec_mtl ts,
		top_sd2.top_1min_mtl tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get Mtl / w3
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'mtl' city_id, 3 wave_id
		,ts.*, tm.wearing
	FROM top_sd3.top_1sec_mtl ts,
		top_sd3.top_1min_mtl tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get Skt / w1
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'skt' city_id, 1 wave_id
		,ts.*, tm.wearing
	FROM top_sd.top_1sec_skt ts,
		top_sd.top_1min_skt tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get Skt / w2
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'skt' city_id, 2 wave_id
		,ts.*, tm.wearing
	FROM top_sd2.top_1sec_skt ts,
		top_sd2.top_1min_skt tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get skt / w3
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'skt' city_id, 3 wave_id
		,ts.*, tm.wearing
	FROM top_sd3.top_1sec_skt ts,
		top_sd3.top_1min_skt tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get van / w1
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'van' city_id, 1 wave_id
		,ts.*, tm.wearing
	FROM top_sd.top_1sec_van ts,
		top_sd.top_1min_van tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get van / w2
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'van' city_id, 2 wave_id
		,ts.*, tm.wearing
	FROM top_sd2.top_1sec_van ts,
		top_sd2.top_1min_van tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get van / w3
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'van' city_id, 3 wave_id
		,ts.*, tm.wearing
	FROM top_sd3.top_1sec_van ts,
		top_sd3.top_1min_van tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get vic / w1
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'vic' city_id, 1 wave_id
		,ts.*, tm.wearing
	FROM top_sd.top_1sec_vic ts,
		top_sd.top_1min_vic tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
  -- Get vic / w2
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'vic' city_id, 2 wave_id
		,ts.*, tm.wearing
	FROM top_sd2.top_1sec_vic ts,
		top_sd2.top_1min_vic tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
-- Get vic / w3
UNION
select city_id, wave_id, interact_id, sd_id
	,min(utcdate) start_time, max(utcdate) end_time
	,max(utcdate) - min(utcdate) survey_duration
	,count(*) n_epoch
	,sum(wearing) n_epoch_wearing
	,count(lat) n_gps_fix
from (
	SELECT 'vic' city_id, 3 wave_id
		,ts.*, tm.wearing
	FROM top_sd3.top_1sec_vic ts,
		top_sd3.top_1min_vic tm
	WHERE ts.interact_id = tm.interact_id AND ts.sd_id = tm.sd_id
		AND date_trunc('minute', ts.utcdate) = tm.utcdate) as foo
group by city_id, wave_id, interact_id, sd_id
```

```{r}
head(top_1s_agg)
```

## Survey time span

```{r}
top_1s_agg |>
  mutate(
    sdate = as_date(start_time),
    edate = as_date(end_time)
  ) |>
  ggplot() +
  geom_segment(
    aes(
      x = sdate,
      xend = edate,
      y = city_id,
      color = city_id
  ),
    linewidth = 2,
    alpha = .3,
    position = position_jitter(width = 0, height = .3)
  ) +
  scale_x_date(name = "Survey period", date_breaks = "2 month", date_labels = "%b %y") +
  facet_wrap(vars(wave_id), ncol = 1, scales = "free", labeller = label_both) +
  theme(legend.position = "none")

```

## Wear time vs total survey time

```{r}
top_1s_agg |>
  ggplot() +
  geom_point(aes(x=n_epoch, y=n_epoch_wearing, color=factor(sd_id))) +
  xlim(0, 10 * 24 * 3600) + ylim(0, 10 * 24 * 3600) + # Define theoretical max of survey n_epoch, i.e. 10 days
  facet_grid(rows = vars(city_id), cols = vars(wave_id)) +
  theme(legend.position = "none")
               
```

```{r}
top_1s_agg |>
  mutate(`Wear time` = n_epoch_wearing / n_epoch) |>
  ggplot() +
  geom_histogram(aes(x = `Wear time`)) +
  scale_x_continuous(labels = scales::percent) +
  facet_grid(rows = vars(city_id), cols = vars(wave_id), scales = "free_y")
```

## Wear time with GPS fix

```{r}
top_1s_agg |>
  ggplot() +
  geom_point(aes(x=n_epoch_wearing, y=n_gps_fix, color=factor(sd_id))) +
  xlim(0, 10 * 24 * 3600) + ylim(0, 10 * 24 * 3600) + # Define theoretical max of survey n_epoch, i.e. 10 days
  facet_grid(rows = vars(city_id), cols = vars(wave_id)) +
  theme(legend.position = "none")
               
```

```{r}
top_1s_agg |>
  mutate(`Wear time with GPS` = pmin(n_gps_fix / n_epoch_wearing, 1)) |>
  ggplot() +
  geom_histogram(aes(x = `Wear time with GPS`)) +
  scale_x_continuous(labels = scales::percent) +
  facet_grid(rows = vars(city_id), cols = vars(wave_id), scales = "free_y")
```

## Step statistcs

Steps have been added in September 2025 following the Bernard Asante's work. Steps are computing according to the Python package `stepcount` (see [repo](https://github.com/OxWearables/stepcount)) based on _Small SR, Chan S, Walmsley R, et al. (2024) Self-Supervised Machine Learning to Characterize Step Counts from Wrist-Worn Accelerometers in the UK Biobank. Medicine & Science in Sports & Exercise. DOI: 10.1249/MSS.0000000000003478_

```{sql, output.var="top_1m", cache=TRUE}
select 'mtl' city_id, 1 wave_id,
  utcdate at time zone 'America/Montreal' datetime,
  wearing, steps, steps_adj
from top_sd.top_1min_mtl
union
select 'skt' city_id, 1 wave_id,
  utcdate at time zone 'America/Regina' datetime,
  wearing, steps, steps_adj
from top_sd.top_1min_skt
union
select 'van' city_id, 1 wave_id,
  utcdate at time zone 'America/Vancouver' datetime,
  wearing, steps, steps_adj
from top_sd.top_1min_van
union
select 'vic' city_id, 1 wave_id,
  utcdate at time zone 'America/Vancouver' datetime,
  wearing, steps, steps_adj
from top_sd.top_1min_vic
union
select 'mtl' city_id, 2 wave_id,
  utcdate at time zone 'America/Montreal' datetime,
  wearing, steps, steps_adj
from top_sd2.top_1min_mtl
union
select 'skt' city_id, 2 wave_id,
  utcdate at time zone 'America/Regina' datetime,
  wearing, steps, steps_adj
from top_sd2.top_1min_skt
union
select 'van' city_id, 2 wave_id,
  utcdate at time zone 'America/Vancouver' datetime,
  wearing, steps, steps_adj
from top_sd2.top_1min_van
union
select 'vic' city_id, 2 wave_id,
  utcdate at time zone 'America/Vancouver' datetime,
  wearing, steps, steps_adj
from top_sd.top_1min_vic
union
select 'mtl' city_id, 3 wave_id,
  utcdate at time zone 'America/Montreal' datetime,
  wearing, steps, steps_adj
from top_sd3.top_1min_mtl
union
select 'skt' city_id, 3 wave_id,
  utcdate at time zone 'America/Regina' datetime,
  wearing, steps, steps_adj
from top_sd3.top_1min_skt
union
select 'van' city_id, 3 wave_id,
  utcdate at time zone 'America/Vancouver' datetime,
  wearing, steps, steps_adj
from top_sd3.top_1min_van
union
select 'vic' city_id, 3 wave_id,
  utcdate at time zone 'America/Vancouver' datetime,
  wearing, steps, steps_adj
from top_sd3.top_1min_vic
```

### All epochs

```{r}
top_1m |>
  select(steps, steps_adj) |>
  summary()
```

```{r}
top_1m |>
  pivot_longer(cols = starts_with("steps"), names_to = "method", values_to = "steps", values_drop_na = T) |>
  ggplot() +
  geom_freqpoly(aes(x = steps, color = method), alpha=.5, lwd=1) +
  scale_color_manual(labels = c("Raw steps", "Adjusted steps"), values = c("blue", "red")) +
  facet_grid(rows = vars(city_id), cols = vars(wave_id)) +
  labs(title = "Step distribution for raw and adjusted steps", x = "Steps / minutes") +
  theme(legend.position = "bottom")
```

```{r}
top_1m |>
  pivot_longer(cols = starts_with("steps"), names_to = "method", values_to = "steps", values_drop_na = T) |>
  filter(steps != 0) |>
  ggplot() +
  geom_freqpoly(aes(x = steps, color = method), alpha=.5, lwd=1) +
  scale_color_manual(labels = c("Raw steps", "Adjusted steps"), values = c("blue", "red")) +
  facet_grid(rows = vars(city_id), cols = vars(wave_id)) +
  labs(title = "Step distribution for raw and adjusted steps | Minutes of zero step removed", x = "Steps / minutes") +
  theme(legend.position = "bottom")
```

### Wearing period epochs

```{r}
top_1m |>
  filter(wearing == 1) |>
  select(steps, steps_adj) |>
  summary()
```

```{r}
top_1m |>
  pivot_longer(cols = starts_with("steps"), names_to = "method", values_to = "steps", values_drop_na = T) |>
  filter(wearing == 1) |>
  ggplot() +
  geom_freqpoly(aes(x = steps, color = method), alpha=.5, lwd=1) +
  scale_color_manual(labels = c("Raw steps", "Adjusted steps"), values = c("blue", "red")) +
  facet_grid(rows = vars(city_id), cols = vars(wave_id)) +
  labs(title = "Step distribution for raw and adjusted steps | Wearing periods only", x = "Steps / minutes") +
  theme(legend.position = "bottom")
```

```{r}
top_1m |>
  pivot_longer(cols = starts_with("steps"), names_to = "method", values_to = "steps", values_drop_na = T) |>
  filter(wearing == 1 & steps != 0) |>
  ggplot() +
  geom_freqpoly(aes(x = steps, color = method), alpha=.5, lwd=1) +
  scale_color_manual(labels = c("Raw steps", "Adjusted steps"), values = c("blue", "red")) +
  facet_grid(rows = vars(city_id), cols = vars(wave_id)) +
  labs(title = "Step distribution for raw and adjusted steps | Wearing periods only, minutes of zero step removed", x = "Steps / minutes") +
  theme(legend.position = "bottom")
```