---
title: "Wave 4 Montreal Linkage"
author: "Zoé Poirier Stephens"
output:
  github_document:
    keep_html: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(kableExtra)
```

# Montreal Wave 4 Linkage Files

### Read in Data

Reading in the data. These are data are relatively different from Wave 1 and 2 as we have a separate file for each of the Polygon, Ethica, and Sensedoc data sources. We are also moving to our naming convention of extract, validate, etc for this document. Here we are reading in three files

- `plg_participants-20250117.csv` which is our main Polygon file
- `study-3729-export-3-participation-2025-01-17-19-32-42.csv` which is our main Ethica file
- `SD_tracking.csv` which is our main Sensedoc file ## FILE IS NOT FINAL! See Marianne in January for final table. 


```{r}
setwd("I:/Benoit/OneDrive - Universite de Montreal/Documents/PROJETS/INTERACT_2016/Donnees/Wave4/Montreal_linkages_w4")

w4_plg <- read_delim("plg_participants-20250117.csv", delim = ",", name_repair = "universal")
w4_eth <- read_delim("study-3729-export-3-participation-2025-01-17-19-32-42.csv", delim = ",", name_repair = "universal")
w4_sd <- read_delim("SD_tracking_not_final2025-02-03.csv", delim = ";", name_repair = "universal")
```

### Validate

Only keep ids of people who have done eligibility 

```{r}

w4_plg <- filter(w4_plg, completed.sessions.count >= 1) 

```

### Rename columns 

```{r}
w4_plg <- rename(w4_plg, 
                 interact_id = study.id,
                 email = identifier, 
                 plg_id = id)

w4_eth <- rename(w4_eth, 
                  ethica_start = Start.Time, 
                  ethica_end = End.Time, 
                  email = Email.Address, 
                  ethica_id = ID)
```

```{r}
w4_plg <- select(w4_plg, interact_id, email, plg_id, status)
```

## Flag deactivated accounts, dropped_out accounts.

Polygon dashboard is how coordinators tracked drop out participants. A drop out on Ethica, is just understood as a drop from that study activity.

(Nota: PLG has different labels to designate a drop out. The plg status 'deactivated' is renamed to dropped out here)

How coordinators used the two statuses at w4: 

+ Désinscrit : Unsubscribed from e-mailings for the Wave. Can contact in future recruitment years.

+ Désactivé : Account deactivated – no longer an INTERACT participant. Do not contact in future years. Includes spam accounts, those no longer living in a study city (or otherwise ineligible), people without valid contact information (e.g., unresponsive, undeliverable email, or invalid phone number), and those requesting to withdraw from the study.

```{r}
w4_plg$dropout <- ifelse(w4_plg$status=="deactivated", 1, 0)


## join PLG with Ethica 
w4_plg$interact_id <- as.character(w4_plg$interact_id)

w4_plg <- full_join(w4_plg, w4_eth, by= "email") 

## join SD to PLG+Ethica

w4_sd$interact_id <- as.character(w4_sd$interact_id)

mtl_w4 <- full_join(w4_plg, w4_sd, by= "interact_id")


```

### Flag Ethica test  

List of test accounts used by our research team to test the Ethica app. These will be flagged later. 

```{r}
ethica_tests <- c("1451", "2036", 
                  "5256", "1454", 
                  "8911", "1469",
                  "1462", "9321", 
                  "12641", "12638", 
                  "12617", "1470",
                  "4579", "5367",
                  "5399","3962")
```

Here we create a 0/1 flag for Ethica test accounts. 

```{r}
mtl_w4 <- mtl_w4 %>%
  mutate(test = ifelse(ethica_id %in% ethica_tests, 1, 0))
```

## add 1 if test accounts 

```{r}
mtl_w4$test[mtl_w4$email == "testlaval@teaminteract.ca"] <- 1
```


### Flag spam accounts

We identified participant accounts suspected of being frequently created to capitalize on the refer-a-friend $10 incentive bonus. These accounts were contacted by email (Notice of Unusual Activity Detected in Study Participation). 
We will exclude these from the final datasets. They are flagged in the linkage table. 

```{r}
## list of spam
fake<- c(404771341, 404519221, 404798627, 404528736, 404558141, 404413088, 404914946)


##flag fake participants from mtl_w4

mtl_w4 <- mtl_w4 %>%
  mutate(spam_participant = ifelse(interact_id %in% fake, 1, 0)) 

```

### Fix unmatched ethica users

```{r}
mtl_w4 <- mtl_w4 |>
  filter(!(ethica_id %in% c(5733, 34388)))
  
mtl_w4[mtl_w4$interact_id == "401545947" & !is.na(mtl_w4$interact_id),"ethica_id"] <- 5733
mtl_w4[mtl_w4$interact_id == "401910133" & !is.na(mtl_w4$interact_id),"ethica_id"] <- 34388

```

### Clean orphan participants

Participant `402781880` collected Sd data but did not complete any survey -> discard

```{r}
mtl_w4 <- mtl_w4 |>
  filter(!(interact_id %in% c("402781880")))
```

### Adding columns

Here we add the columns to have consistent columns across linkage files. 

```{r}
mtl_w4$data_disposition <- NA
mtl_w4$treksoft_pid <- NA
mtl_w4$treksoft_uid <- NA
mtl_w4$wave <- 4
```

### Selecting variables

```{r}
mtl_w4 <- select(mtl_w4, interact_id, treksoft_pid, treksoft_uid, ethica_id, sd_id_1, sd_firmware_1, sd_start_1, sd_end_1, sd_id_2, sd_firmware_2, sd_start_2, sd_end_2, data_disposition, plg_id, dropout, wave, test, spam_participant)
```

## Write clean csv file

```{r, eval = TRUE}
write.csv(mtl_w4, file = "linkage_mtl_w4.csv")
```
