---
title: "Wave 1 Saskatoon Linkage"
author: "Daniel Fuller"
output:
  github_document:
    keep_html: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(kableExtra)
```

# Saskatoon Wave 1 Linkage Files

### Read in Data

Reading in the data. Here we are reading in two files

- `linkage_for_ingest_skt_w1.csv` which is our main file
- `lut_skt.csv` which is a look up table for looking up previous versions of the health and VERITAS ID variables. These will not be used after Wave 1. 

```{r, eval = FALSE, echo = FALSE}
setwd("/Users/dlf545/Documents/ForDan_Linkages_072023")
```

```{r}
setwd("/Users/dlf545/Documents/ForDan_Linkages_072023")
skt <- read_delim("linkage_for_ingest_skt_w1.csv", delim = ";")
lut_skt <- read_delim("lut_skt.csv", delim = ",")

skt_w1 <- full_join(skt, lut_skt, by="interact_id")
```

## Ethica test accounts

List of test accounts used by our research team to test the Ethica app. These will be flagged later. 

```{r}
ethica_tests <- c("1451", "2036", 
                  "5256", "1454", 
                  "8911", "1469",
                  "1462", "9321", 
                  "12641", "12638", 
                  "12617", "1470",
                  "4579", "5367",
                  "5399","3962")
```

## Cleaning up dates

There are problems with SD dates in Saskatoon Wave 1  

- this file: `linkage_for_ingest_skt_w1.csv` has wrongly encoded dates, but generally 9 day periods. Dates in 2010. This is what Jeff used. I believe this is correct data. 
- this file: `Participant_Tracking_SASK_W1-norm-filtered-redated.csv` has 11-day SD periods, correctly encoded, but I think are the wrong dates. Just an automated +11 rule on excel. 

```{r}


```

### Add treksoft IDs 

Here we are adding the Treksoft (Health and VERITAS) IDs to the data. These are `treksoft_pid` and `treksoft_uid`. 

```{r}
skt_w1 <- select(skt_w1, interact_id, treksoft_pid, treksoft_uid, ethica_id.x, sd_id_1, sd_firmware_1, sd_start_1, sd_end_1, sd_id_2, sd_firmware_2, sd_start_2, sd_end_2, dropout, data_disposition, test)
```

### Rename ethica 

```{r}
skt_w1 <- rename(skt_w1, ethica_id = ethica_id.x)
```

### Flag Ethica test  

Here we create a 0/1 flag for Ethica test accounts. 

```{r}
skt_w1 <- skt_w1 %>%
  mutate(test = ifelse(ethica_id %in% ethica_tests, 1, 0)) 
```

### Adding columns

Here we add the columns 

- `plg_id`: This is a ID column that will supersede the `treksoft_pid` and `treksoft_uid`. Note that the company Treksoft and Polygone are the same, they just changed names during the study period. 
- `wave`: The wave ID for the study.

```{r}
skt_w1$plg_id <- NA
skt_w1$wave <- 1
```

## Write clean csv file

```{r, eval = FALSE}
write.csv(skt_w1, file = "linkage_skt_w1.csv")
```





